Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Add testpack to "related work"

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open problems and related work}

literate programming.

hunit.

test-framework.

smallCheck.

And others?

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open problems and related work}
\begin{itemize}
    \item literate programming.
    \item hunit.
    \item test-framework.
    \item smallCheck.
    \item And others?
    \item The {\tt testpack} package provides a function that is
        similar in purpose to {\tt shouldThrow}.

        @kazu: Do you think we should discuss this; or is it safe to
        ignore.

\begin{quote}\small\begin{verbatim}
assertRaises :: (Show a, Exception e, Show e, Eq e) =>
  String -> e -> IO a -> IO ()
\end{verbatim}\end{quote}
        But it has several shortcomings:
        \begin{itemize}
            \item
                It only works for exceptions with an {\tt Eq}
                instance, but several standard exceptions (most
                prominently {\tt ErrorCall}) have no {\tt Eq}
                instance.
            \item
                It places an unnecessary {\tt Show} constraint on the
                result of the {\tt IO} action, further limiting it's
                applicability.
            \item
                It only allows to expect specific values; expecting
                any exception of a certain type is not possible.
        \end{itemize}
\end{itemize}
